---
title: "distill 패키지 - R 기반 블로그"
output: html_document
---

# 개요

-   distill 패키지 소개
-   블로그 포스팅 하기
-   카테고리 링크 하기
-   블로그 빌드 하기
-   블로그 배포

# distill package 소개

```{r}
if ( !require("distill") ) {
  install.packages("distill")  
}
library(distill)
```

# 블로그 만들기

```{r}
dir_   <- "Hoony"
title_ <- "Hoony's Archieve"
create_blog(dir = dir_, title = title_, gh_pages = TRUE)

```

# 블로그 설정

After you've created the blog scaffolding, there are a couple of additional configuration items you'll want to add to your `_site.yml` so that it's easier to share content on the blog via RSS and social networks like Twitter:

-   A short `description` of the site. This field is used for the channel description of your RSS feed.

-   A `base_url` for the site (the URL where it will be published to). This is used both for RSS feed items and for sharing posts via [Open Graph](https://rstudio.github.io/distill/metadata.html#open-graph) and [Twitter Card](https://rstudio.github.io/distill/metadata.html#twitter-card).

For example:

**\_site.yml**

    name: "reproducible-finance-with-r"
    title: "Reproducible Finance with R"
    description: |
      Exploring reproducible finance with the R statistical 
      computing environment.
    base_url: https://beta.rstudioconnect.com/content/11424/
    navbar:
      logo: images/rstudio.png
      right:
        - text: "Home"
          href: index.html
        - text: "About"
          href: about.html
        - text: "Contributors"
          href: contributors.html
        - icon: fa fa-rss
          href: index.xml
    output: distill::distill_article

Note that we've also added a feed icon to the right side of the menu bar which makes it easy to discover and browse the RSS feed for the blog.

# 블로그 포스팅 하기

```{r}


```

# 카테고리 만들기

```{r}


```

# 블로그 빌드

```{r}


```

# github homepage 배포

```{r}


```
